---
title: "Climate Security"
bibliography: references.bib
csl: "apa-6th-edition.csl"
output: 
   html_document:
    toc: true
    toc_float: true
    toc_collapsed: true
    toc_depth: 3
    number_sections: false
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

*Climate security* refers to any **threats or risks to states, societies, and individual citizens directly or indirectly caused by climate change**. Climate variability and climate extreme events are impacting food, land and water systems thereby threatening agriculture productivity, and diminishing natural resources of land and water, which increases resource-based conflicts. 

## IOM GTM Project

[Click here](GTM_iom.html)

## Ethiopia

Ethiopia is considered one of the most susceptible countries to climate change-related shocks, including droughts, floods, and desert locust infestation, leading to massive losses. This vulnerability also stems from political, socioeconomic, and geographic conditions, which remain unfavourable. Agriculture is critical to the National GDP, accounting for 40\% of the GDP while employing 78\% of the workforce. It is considered a least developed country with more than 100 million population. Nearly 80\% of the population lives in the rural area practicing smallholder farming.  

- *High conflict versus other climate categories*

```{r E1, message=F, warning=F, echo=F}
#https://r.geocompx.org/adv-map.html
library(terra)
root <- 'D:/OneDrive - CGIAR/Analysis/CSO/'
iso <- 'ETH'
conf <- geojsonio::geojson_sf(paste0(root,iso,'/clim_conflict_ips_overlays.geojson'))
conf <- subset(conf, intersect_conf_clim != "Limited conflict-[NA]" & intersect_conf_clim != "High conflict-[NA]")
temp <- conf[conf$conflict_clust_label=="High conflict"  ,]
temp <- temp[temp$intersect_conf_clim !="High conflict-[NA]",] 
i <- temp$intersect_conf_clim

temp$intersect_conf_clim[i=="High conflict-[High levels of precipitation/Low levels of Heat stress]"] <-
  "High conflict + Low heat stress"
temp$intersect_conf_clim[i=="High conflict-[Moderate levels of precipitation/moderate levels of Heat stress]"] <-
  "High conflict + Moderate heat stress"
temp$intersect_conf_clim[i== "High conflict-[Low levels of precipitation/High levels of Heat stress]"] <-
  "High conflict + High heat stress" 

i <- temp$intersect_conf_clim
temp$clust[i=="High conflict + Low heat stress"] <- 3
temp$clust[i=="High conflict + Moderate heat stress"] <- 2
temp$clust[i=="High conflict + High heat stress"] <- 1
temp$clust <- as.factor(temp$clust)
labs <- c("High conflict + High heat stress","High conflict + Moderate heat stress",
          "High conflict + Low heat stress") 

bdy1 <- geodata::gadm(country=iso, level=1, path=paste0(root,iso,'/'))
bdy1 <- sf::st_as_sf(bdy1)
bdy2 <- geodata::gadm(country=iso, level=2, path=paste0(root,iso,'/'))
bdy2 <- sf::st_as_sf(bdy2)
bdy3 <- geodata::gadm(country=iso, level=3, path=paste0(root,iso,'/'))
bdy3 <- sf::st_as_sf(bdy3)
temp$Woreda <- temp$NAME_3
library(tmap)
library(mapview)
tmap_mode("view")
et <- tm_shape(bdy1, name = 'Region')+
  tm_borders() +
  tm_shape(bdy2, name = 'Zone')+
  tm_borders() +
  tm_shape(bdy3, name = 'Woreda')+
  tm_borders()+
  #tm_text('NAME_3')+
  tm_shape(temp, name = 'Conflict')+
  tm_fill(col= "clust", palette="-YlOrRd", title = 'Climate-Conflict-Hotspots', labels=labs, popup.vars=c("Woreda", "FATALITIES", "climvar_medn_prec", "livelihoods", "female_population", "male_population", "median_male_female_edu_diff"))+
  #tm_dots(size='FATALITIES', col='blue')+
  tm_format("World")
et 


```


## Sudan

Sudan is a signatory to UNFCCC and is committed to the Paris Agreement. It has developed enabling policies and legislative frameworks to deal with climate change and fulfil its international commitments. Key among them is the National Adaptation Plan and the Updated NDC 2022. According to the Updated NDC 2022, Sudan is committed to reducing greenhouse gas emissions by 38\% in the energy sector (12.4 Mt CO2e), 45% in the forestry sector (13.4 Mt CO2e), and 20% in the waste sector (1.3 Mt CO2e) by 2030 compared to business-as-usual, conditional on external support. Due to its high level of vulnerability, climate adaptation remains its highest priority, focusing on agriculture, water, health and coastal zones. Over the next ten years, Sudan will require 8.24 billion USD to implement its priority mitigation and adaptation measures. 

- *High conflict versus other climate categories*

```{r S1, message=F, warning=F, echo=F}
iso <- 'SDN'
conf <- geojsonio::geojson_sf(paste0(root,iso,'/clim_conflict_ips_overlays.geojson'))
bdy1 <- geodata::gadm(country=iso, level=1, path=root)
bdy1 <- sf::st_as_sf(bdy1)
bdy1 <- sf::st_cast(bdy1)  
bdy2 <- geodata::gadm(country=iso, level=2, path=paste0(root,iso,'/'))
bdy2 <- sf::st_as_sf(bdy2)
bdy3 <- geodata::gadm(country=iso, level=3, path=paste0(root,iso,'/'))
bdy3 <- sf::st_as_sf(bdy3)
temp <- conf[conf$conflict_clust_label=="High conflict"  ,]
i <- temp$intersect_conf_clim
temp$intersect_conf_clim[i=="High conflict-[High levels of precipitation/Low leves of  drought stress]"] <-
  "High conflict + Low drought stress" 
temp$intersect_conf_clim[i=="High conflict-[Moderate levels of precipitation/Moderate levels drought stress]"] <-
  "High conflict + Moderate drought stress"
temp$intersect_conf_clim[i=="High conflict-[Low levels of precipitation/High levels drought stress]"] <-
 "High conflict + High drought stress"
i <- temp$intersect_conf_clim

temp$clust[i=="High conflict + Low drought stress"] <- 3
temp$clust[i=="High conflict + Moderate drought stress"] <- 2
temp$clust[i=="High conflict + High drought stress"] <- 1
temp$clust <- as.factor(temp$clust)
labs <- c("High conflict + High drought stress","High conflict + Moderate drought stress",
          "High conflict + Low drought stress")


temp$Bomas <- temp$NAME_3
library(tmap)
library(mapview)
tmap_mode("view")
sdn <- tm_shape(bdy1, name = 'State')+
  tm_borders() +
  tm_shape(bdy2, name = 'District')+
  tm_borders() +
  tm_shape(bdy3, name = 'Bomas')+
  tm_borders()+
  tm_shape(temp, name = 'Conflict')+
  tm_fill(col= "clust", palette="-YlOrRd", title = 'Climate-Conflict-Hotspots', labels=labs, popup.vars=c("Bomas", "FATALITIES", "climvar_medn_prec", "livelihoods", "female_population", "male_population", "median_male_female_edu_diff"))+
  tm_format("World")
sdn 


```



